Differential invariant signatures for planar Lie group transformations of images

### 2020-11-10 paper/newpaper.tex
now

\item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Equation~(\ref{eqn:mobius}); it is:
$$\bar f_{bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
\end{enumerate}

@@

The four third-order invariants can be deduced from the moving frame. They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.  Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
$M_2=
f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
 f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
 9 f_y ^3 f_{yy} f_x  f_{xy} + 
 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 - 
 9 f_y ^2 f_x ^2 f_{xy}^2 + \frac{3}{2} f_z ^4 f_{xy}^2 + 
 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
 3 f_y ^3 f_x  f_{xy} f_{xx} - 
 9 f_y  f_x ^3 f_{xy} f_{xx} + \frac{3}{2} f_y ^4 f_{xx}^2 + 
 \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
 f_x ^5 f_{xxx}, 
 $

 $M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
 f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
 6 f_y  f_x ^3 f_{xy}^2 - 3 f_y ^3 f_x ^2 f_{xyy} - 
 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
 9 f_y ^2 f_x ^2 f_{xy} f_{xx} + 
 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
 f_y ^3 f_x ^2 f_{xxx}.
$

@@

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\label{eq:prolong}
%\rotatebox{90}{$
\left[
\begin{array}{c}
  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar x \bar x} \\ \bar f_{\bar x \bar y} \\ \bar f_{\bar y \bar y} \\ \bar f_{\bar x \bar x \bar x} \\ \bar f_{\bar x \bar x \bar y} \\ \bar f_{\bar x \bar y \bar y} \\ \bar f_{ \bar y \bar y \bar y} 
 \end{array}
 \right]
 = 
\left[
\begin{array}{ccccccccc}
 a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 2 g \alpha_1 & 2 g \beta_1 & -2 a \alpha_2 & -4 \delta_1 & -2 c \beta_2
   & a^2 b & a \gamma_1 & c \gamma_1 & c^2 d \\
 2 h \alpha_2 & 2 h \beta_2 & -2 b \alpha_1 & -4 = \delta_2 & -2 d \beta_1
   & a b^2 & b \gamma_1 & d \gamma_2 & c d^2 \\
 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
\end{array}
\right]\left[
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right].%$}
 \end{equation}

>>>>

\item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Equation~(\ref{eqn:mobius}); it is:
$$\bar f_{\bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
\end{enumerate}

@@

The four third-order invariants can be deduced from the moving frame. They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.  Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
$$M_2=
f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
 f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
 9 f_y ^3 f_{yy} f_x  f_{xy} + 
 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 - 
 9 f_y ^2 f_x ^2 f_{xy}^2 + \frac{3}{2} f_z ^4 f_{xy}^2 + 
 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
 3 f_y ^3 f_x  f_{xy} f_{xx} - 
 9 f_y  f_x ^3 f_{xy} f_{xx} + \frac{3}{2} f_y ^4 f_{xx}^2 + 
 \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
 f_x ^5 f_{xxx}, 
 $$

 $$M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
 f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
 6 f_y  f_x ^3 f_{xy}^2 - 3 f_y ^3 f_x ^2 f_{xyy} - 
 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
 9 f_y ^2 f_x ^2 f_{xy} f_{xx} + 
 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
 f_y ^3 f_x ^2 f_{xxx}.
$$

@@

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\label{eq:prolong}
%\rotatebox{90}{$
\left[
\begin{array}{c}
  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar x \bar x} \\ \bar f_{\bar x \bar y} \\ \bar f_{\bar y \bar y} \\ \bar f_{\bar x \bar x \bar x} \\ \bar f_{\bar x \bar x \bar y} \\ \bar f_{\bar x \bar y \bar y} \\ \bar f_{ \bar y \bar y \bar y} 
 \end{array}
 \right]
 = 
\left[
\begin{array}{ccccccccc}
 a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 2 g \alpha_1 & 2 g \beta_1 & -2 a \alpha_2 & -4 \delta_1 & -2 c \beta_2
   & a^2 b & a \gamma_1 & c \gamma_1 & c^2 d \\
 2 h \alpha_2 & 2 h \beta_2 & -2 b \alpha_1 & -4 \delta_2 & -2 d \beta_1
   & a b^2 & b \gamma_1 & d \gamma_2 & c d^2 \\
 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
\end{array}
\right]\left[
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right].%$}
 \end{equation}
